*Appendix A2*

### 2022-07-21 ms/si2.Rmd
Update MS
Update SI2

---
title: "*Supplementary Material 2*"
subtitle: "Fossil Calibration List"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "frontiers.csl"]
  bookdown::word_document2:
    pandoc_args: [ "--csl", "frontiers.csl"]
    toc: no
    number_sections: no
    reference_docx: Frontiers_Template_SI.docx
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Supplementary Material 2} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \setlength{\headheight}{13.6pt}
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: manual
---

---
bibliography: 
- `r here::here("ms/si_fossils.bib")`
---

@@

# Targets from MS workflow
tar_load(
  c(
    fossil_notes,
    fossil_meta),
  store = here::here("_targets")
)
```

@@

Taxonomy of extant taxa follows pteridocat v0.0.1 database (https://github.com/fernphy/pteridocat).

>>>>

---
title: "*Appendix A2*"
subtitle: "Fossil Calibration List"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "frontiers.csl"]
  bookdown::word_document2:
    pandoc_args: [ "--csl", "frontiers.csl"]
    toc: no
    number_sections: no
    reference_docx: Frontiers_Template_SI.docx
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Appendix A2} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \setlength{\headheight}{13.6pt}
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: manual
---

---
bibliography: 
- `r here::here("ms/ferncal_references.yaml")`
---

@@

# Targets from MS workflow
tar_load(
  c(fossil_meta,
    ref_files),
  store = here::here("_targets")
)
```

@@

Taxonomy of extant taxa follows pteridocat v1.0.0 database (https://github.com/fernphy/pteridocat).
